How did Covid-19 affect the number of marriages

### 2024-09-24 paper/paper.qmd
Initial push

---
title: "How did Covid-19 affect the number of marriages"
subtitle: "Evidence from the Toronto"
author: 
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/RohanAlexander/marriage."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @kjlaskjasdnaf.

>>>>

---
title: "How did Covid-19 affect the number of marriages"
subtitle: "Evidence from Toronto"
author: 
  - Justin (Jiazhou) Bi
thanks: "Code and data are available at: https://github.com/RohanAlexander/marriage."
date: Sept. 23, 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
jupyter: python3 
number-sections: true
bibliography: references.bib
---

```{python}
#| include: false
#| warning: false
#| message: false

import pandas as pd
# import numpy as np
import matplotlib as plt
# import seaborn as sns

data = pd.read_csv('/Users/jiazhoubi/Desktop/UT MI/INF 3104/reported-crime/data/analysis_data/analysis_data.csv')
data.head()
```

@@

You can and should cross-reference sections and sub-sections. We use @Python3 and @TorontoOpenData.
